Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2021-09-02 paper/SupMat.Rnw
a few more changes to finally make Sweave work on my machine. depends on jasmin changing the pdf file names so they don't include a . other than the one right bfore the extension
added section to sup mat for delta=1

\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

&= -\E[\ln(1-\delta+\delta \exp(\sigma (\tilde{b}_j^\shp - \tilde{b}_j)))],

@@

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}
%\SweaveOpts{concordance=TRUE}

@@

&= -\E[\ln(1-\delta+\delta \exp(\sigma (\tilde{b}_j^\shp - \tilde{b}_j)))],\label{eq:decomp:j:pECp}

@@

\section{The $\delta=1$ case}\label{sect:delta1}

%The i terms
Setting $\delta=1$ in (\ref{eq:decomp:baseline}) gives 
\begin{equation}
\epsilon_i^0 = \mu_i - \mu_j.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_of_var_E}) gives
\begin{align}
\olep_i^E &= \mu_i-\mu_j-\sigma^2/2-\epsilon_i^0 \\
&= -\sigma^2/2.
\end{align}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_of_var_C}) gives
\begin{align}
\olep_i^C &= \mu_i - \mu_j + \sigma^2/2 -\epsilon_i^0 \\
&= \sigma^2/2.
\end{align}
Setting $\delta=1$ in (\ref{eq:decomp:last_term_primary}) gives
\begin{align}
\olep_i^{EC} &= \mu_i - \mu_j -\olep_i^E - \olep_i^C - \epsilon_i^0 \\
&= 0.
\end{align}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_of_EC_var_per_se}) gives
\begin{align}
\olep_i^{(E \shp C)} &= \mu_i - \mu_j -\olep_i^E - \olep_i^C - \epsilon_i^0 \\
&= 0.
\end{align}
Setting $\delta=1$ in (\ref{eq:decomp:storage_effects}) gives
\begin{align}
\olep_i^{(EC)} &= \mu_i - \mu_j - (\mu_i -\mu_j) \\
&= 0.
\end{align}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_ATA_2}) gives
\begin{equation}
\olep_i^{[E \nat C]}=0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_EC}) gives
\begin{equation}
\olep_i^{[EC]}=0.
\end{equation}
%The j terms
Setting $\delta=1$ in (\ref{eq:decomp:baseline_j}) gives
\begin{equation}
\epsilon_j^0 = 0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_of_var_E_j}) gives
\begin{equation}
\olep_j^E = -\sigma^2/2.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:contrib_of_var_C_j}) gives
\begin{equation}
\olep_j^C = \sigma^2/2.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:j:EC}) gives
\begin{equation}
\olep_j^{EC} = 0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:j:EshpC}) gives
\begin{equation}
\olep_j^{(E \shp C)} = 0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:j:pECp}) gives
\begin{equation}
\olep_j^{(EC)} = 0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:j:EnatC}) gives
\begin{equation}
\olep_j^{[E \nat C]} = 0.
\end{equation}
Setting $\delta=1$ in (\ref{eq:decomp:j:EChard}) gives
\begin{equation}
\olep_j^{[EC]}=0.
\end{equation}

For $\delta=1$, the second value of $q_{ij}$ we considered, namely
$q_{ij}=\frac{\exp(\mu_i)}{(1-\delta)\exp(\mu_j)+\delta \exp(\mu_i)}$, equals $1$, so both the
options we considered for $q_{ij}$ are $1$ in this case. Combining the above 
equations using $q_{ij}=1$ gives
\begin{align}
\Delta_i^0 &= \mu_i - \mu_j \\
\Delta_i^E &= 0  \\
\Delta_i^C &= 0  \\
\Delta_i^{(E \shp C)} &=  0 \\
\Delta_i^{[E \nat C]} &= 0  \\
\Delta_i^{[EC]} &=  0. 
\end{align}
Thus the only contribution to coexistence for the $\delta=1$ case is $\Delta_i^0 = \mu_i - \mu_j$,
which does not depend on $\sigma$ and which is non-positive whenever $\mu_i \leq \mu_j$ (which we assumed,
without loss of generality).
So there is no robust coexistence in the $\delta=1$ case for our simple model.
